My title

### 2024-04-19 paper/paper.qmd
don't remember what I did, but I think updating files so that the tables run

cleaned_data_NKE <- read.csv("../data/analysis_data/cleaned_data_NKE.csv")
cleaned_data_PRKS <- read.csv("../data/analysis_data/cleaned_data_PRKS.csv")
```

>>>>

cleaned_data_NKE <- read.csv("../data/analysis_data/cleaned_data_NKE.csv")
cleaned_data_NKE <- 
  cleaned_data_NKE |>
  mutate(Date = lubridate::ymd(Date))
cleaned_data_NKE$Date <- 
  as.Date(cleaned_data_NKE$Date, format='%Y-%m-%d')

cleaned_data_PRKS <- read.csv("../data/analysis_data/cleaned_data_PRKS.csv")
```
